Surrogate waveform model using Gaussian process regression for an aligned-spin effective one body model of binary neutron star inspirals

### 2018-10-17 paper/paper.tex
Adding PE discussion to paper. Fixing coalescence time problem with LAL version.

\begin{figure*}[htb]
\centering
\includegraphics[width=0.99\textwidth]{hmaxerror.pdf}
\caption{Inverse Fourier transformed surrogate (red dashed) for the parameters $\{q, \chi_1, \chi_2, \Lambda_1, \Lambda_2\} = \{0.61, -0.23, -0.33, 180, 4390\}$ that have the largest mismatch with the test-set EOB waveforms (black). The two waveforms are aligned in the time domain, before the start of the plot, in the interval $(t-t_{\rm merger})/M \in [-10^7, -10^6]$.}
\label{fig:maxmismatchtd}
\end{figure*}

@@

>>>>

\begin{figure*}[htb]
\centering
\includegraphics[width=0.99\textwidth]{hmaxerror.pdf}
\caption{Inverse Fourier transformed surrogate (red dashed) for the parameters $\{q, \chi_1, \chi_2, \Lambda_1, \Lambda_2\} = \{0.61, -0.23, -0.33, 180, 4390\}$ that have the largest mismatch with the test-set EOB waveforms (black). The two waveforms are aligned in the time domain, before the start of the plot, in the interval $(t-t_{\rm Merger})/M \in [-10^7, -10^6]$.}
\label{fig:maxmismatchtd}
\end{figure*}

@@

Having confirmed that the surrogate accurately recovers the injected waveform parameters, we now perform a parameter estimation run for GW170817. In the PE paper and catalog papers~\cite{}, the SEOBNRv4T surrogate was used with the parallelized PE code RapidPE. However, there were uncertainties about its ability to accurately recover the tidal parameter.

We use the priors discussed in~cite{O2CatalogPaper}.
